Community-Conditioned Language Models

### 2020-11-20 paper/paper.tex
related work intro

>>>>

In this work, we present results using a conditioned neural language models
to model variation between speech communities.
The architecture of these models concatenates a vector representation
of the conditioned variable to the input of the sequence model.
This approach has been applied in various conditioned text generation domains such as 
image captioning \citep{Vinyals2015}, machine translation \citep{Kalchbrenner2013},
but it has not, to our knowledeg, been used extensively to study linguistic variation.
There are, however some related methods that have been used to study variation,
and related applications of conditional neural language models.

In the later category, conditoinal nerual language models have been used to study linguistic change.
